---
title: "leaflet-project"
author: "Ly Nguyen"
date: "9/19/2020"
output: html_document
---

## Introduction 
For this exercise, I would like to create a interactive map of Vietnam's coastal region, which shows Vietnam's 9 coastal provinces. Some of these are popular tourist destinations, this map will indicate some information on these provinces and their tourist arrivals. 

## Load our data 
```{r echo=TRUE}
library(readxl)
setwd("C:/Users/Ly Nguyen/Learning/Courses/John Hopkins - R/9. Developing Data Products/Markdown-leaflet-project")
tourism <- read_excel("data/tourism.xlsx")
tourism
```
This data set contains names of the 9 coastal provinces, their location, their capital city, their geographical area & lastly, their population. 

## Let's make an interactive map with leaflet 
```{r echo=TRUE, fig.align='center', fig.height=8, fig.height=8}
library(leaflet)
library(sp)
library(htmltools)

content <- paste0('<strong>Province: </strong>',tourism$Province, '<br><strong>Population (thousands people): </strong>', tourism$Pop_thousand, '<br><strong>Capital City: </strong>', tourism$Capital)
legText <- paste0('The relative size of the circles<br>on the map shows that for provinces<br>such as <strong>Da Nang, Hue & Khanh Hoa</strong>,<br>the amount of tourists outpaces<br>the area of the province,<br>suggesting a possible overdemand<br>for tourism & strain on the province capacity.<br><br>On the other hand, provinces such as <br><strong>Quang Tri, Quang Ngai & Phu Yen</strong><br>have not become tourist destinations<br>and their potential should not be overlooked.')

myMap <-tourism %>% 
        leaflet() %>% 
        addTiles() %>%
        addLegend(labels=c("Tourist Arrivals (Millions)", "Province Area (thousand ha)"), colors = c("darkslategray","darkred"), values=tourism$`Tourist Arrivals_millions`) %>%
        addCircles(lng=tourism$Long, lat=tourism$Lat, radius=tourism$`Tourist Arrivals_millions`*8000, color = "darkslategray", weight=2) %>% 
        addCircles(lng=tourism$Long, lat=tourism$Lat, 
                         radius=tourism$`Area_ thousand ha`*30, 
                         label=lapply(content, HTML), 
                         color="darkred", opacity=0.5, fill=TRUE, weight=2) %>%
        addPopups(lat=14.399616, lng=111.224435, popup=lapply(legText, HTML), 
                  options = popupOptions(autoPan=T, closeOnClick = F, closeButton=T))
myMap
```
In the above popup, I explain briefly the insights I got from creating this simple map. 

Enjoy. 



